\subsection{Matrix-Based Separation Facility Model}

By describing the separations process as a simple matrix of efficiencies, a  
material stream transformation can be conducted. The specific process chemistry 
for the separation at hand is treated as elemental, as representative of a 
  non-laser separations process. The efficiencies must be defined to transform 
  an incoming composition vector $I$ with $N$ constituent amounts, $I_n$ to an 
  outgoing set of $M$ streams, $E_m$. The efficiency matrix $\eta$ is therefore 
  an $N\times M$ matrix of efficiencies. The matrix of separation efficiencies 
  has a default value: the identity matrix of size $N\times N$. In this 
  context, the identity matrix represents complete and perfect elemental 
  separation without losses. 

\begin{align}
  \left[
    \begin{array}{c c c c c c c}
      \eta_{11} & . & . & . & . & . & \eta_{1M} \\
      \eta_{21} & . & . & . & . & . & \eta_{2M} \\
      . & . & . & . & . & . & . \\
      . & . & . & . & . & . & . \\
      . & . & . & . & . & . & . \\
      \eta_{N1} & .  & . & . & . & . & \eta_{NM} \\
    \end{array}
    \right]
  \left[
    \begin{array}{c}
      I_1\\
      I_2\\
      . \\
      . \\
      . \\
      I_N\\
    \end{array}
    \right]
    =
    \left[
      \begin{array}{ c }
        E_1\\
        E_2\\
        .\\
        .\\
        .\\
        E_M\\
      \end{array}
      \right]
\label{defaultsep}
\end{align}

For realistic separations, the user is expected to produce an efficiency 
matrix representing the separations technology of interest to them. 
By requesting the feedstock from the 
appropriate markets, the facility acquires an unseparated feedstock stream. 
Based on the input parameters  in Table \ref{tab:sepmatrix}, the separations 
process proceeds within the timesteps and other constraints of the simulation. 

\begin{table}[h!]
\centering
\begin{tabular}{|l|r|r|r|}
\hline
\textbf{Parameter} & \textbf{Units} & \textbf{Default} & \textbf{Range}\\ 
\hline
In-Commodity & string &``'' & any string \\
$\eta$ Matrix & \% yield & Identity & positive matrix \\
\hline
\end{tabular}
\caption{Input parameters for the Matrix-Based Separation Facility Model}
\label{tab:sepmatrix}
\end{table}

Thereafter, separated streams as well as a stream of losses are offered the 
appropriate markets for consumption by other facilities. In the transition 
scenario at hand, the StreamBlender fuel fabrication facility purchases the 
streams it desires in order to produce SFR fuel. 
